%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
%---------------------------------------------------------
  \cventry
    {University of Regina} % Organization
    {Mobile Application Developer} % Job Title
    {Regina, Canada} % Location
    {January 2020 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Digitalized paper-based safety forms on the Android Platform.}
        \item {Created an application using KOTLIN as a programming language.}
        \item {Created REST API using Python Flask to communicate with MySQL Database.}
        \item {Implemented Material Design concepts for UI/UX development.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {ExxonMobil} % Organization
    {End-User System Analyst} % Job Title
    {Calgary, Canada} % Location
    {September 2018 - April 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed SharePoint based AppStore using Nintex form and workflow, JavaScript, and SharePoint Web Services to replicate the custom solutions.}
        \item {Worked in Agile Kanban software development environment.}
        \item {Handled client communication for project critical development.}
        \item {Worked with the Data Science team to develop custom Machine Learning models.}
      \end{cvitems}
    }


%---------------------------------------------------------

 \cventry
    {Digiways} % Organization
    {Web Developer} % Job Title
    {Mehsana, India} % Location
    {November 2016 - January 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed an improved PHP and MySQL database based order and client management system.}
        \item {Developed and redesigned MySQL based email system for clients' inquiries.}
        \item {Designed for and tested desktop and mobile sites, across multiple browsers.}
        \item {HTML, CSS, Javascript, and Bootstrap front-end development.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
